\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-12 papers/jss/article.Rnw
some rephrasing on int64
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@760 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

R does not have native 64-bit integer support.  Instead, R treats
large integers as doubles which have limited precision.  For example,
it loses the ability to distinguish some distinct integers:

@@

Protocol Buffers are frequently used to pass data between different
systems, however, and most other modern systems do have support for
64-bit integers.  To work around this, RProtoBuf allows users to get
and set 64-bit integer types by treating them as characters.

@@

However, we can specify the values as character strings so that the
C++ library on which RProtoBuf is based can store a true 64-bit
integer representation of the data.

>>>>

R also does not support the native 64-bit integer type. Numeric vectors
with values $\geq 2^{31}$ can only be stored as doubles, which have
limited precision. Thereby R loses the ability to distinguish some
distinct integers:

@@

However, most modern languages do have support for 64-bit integers, 
which becomes problematic when \pkg{RProtoBuf} is used to exchange data 
with a system that requires this integer type. To work around this, 
RProtoBuf allows users to get and set 64-bit integer values by specifying 
them as character strings.

@@

But when the values are specified as character strings, RProtoBuf
will automatically coerse them into a true 64-bit integer types 
before storing them in the Protocol Buffer message:
